DATA 621 - Business Analytics and Data Mining

### 2020-11-02 HW4/HW4_Draft.Rmd
Model1 for freq

```{r loadData, include=FALSE}
# Load necessary libraries
library(corrplot)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(data.table)
# Set master seed
set.seed(71554)

@@

### Dummy Variables
As there are many factor variables, dummy variables will be created. The target
variables will be removed and held to the side so as not to contaminate the
fitting

```{r model1createDummy}
trnFreq <- tstX$TARGET_FLAG
trnSev <- tstX$TARGET_AMT
tstDumFreq <- TARGET_FLAG ~ . - c(INDEX, TARGET_AMT)
```

# BUILD MODELS
## Model Set 1
### Frequency Model
The frequency model will be a binary logistic on the prepared data. It will
start with the complete model and allow for some interactions. It will use both
forward and backward steps to identify which variables to include, using AIC as
the test metric. Using this approach does not allow for cross-validation. The
initial interactions considered will be:

 * `OWN` with `HOME_VAL` as discussed above
 * `HOME_VAL` with `INCOME` as using both may overstate the effect of wealth
 * `KIDSDRIV` with `HOMEKIDS` as there is

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r zeroVal}
```
```{r statsN}
```
```{r graphsN}
```
```{r graphsF}
```
```{r dataClean}
```
```{r trainTestSplit}
```
```{r model1addVars}
```

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(corrplot)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(data.table)
# Set master seed
set.seed(71554)

@@

# BUILD MODELS
## Model Set 1
### Dummy Variables
As there are many factor variables, dummy variables will be created. The target
variables will be removed and held to the side so as not to contaminate the
fitting.

### Frequency Model
The frequency model will be a binary logistic on the prepared data. It will
start with the complete model and allow for some interactions. It will use both
forward and backward steps to identify which variables to include, using AIC as
the test metric. Using this approach does not allow for cross-validation. The
initial interactions considered will be:

 * `OWN` with `HOME_VAL` as discussed in the missing data section
 * `KIDSDRIV` with `HOMEKIDS`
 * A three-way interaction between `HOME_VAL`, `INCOME`, and `BLUEBOOK`
 * `CLM_FREQ` with `OLDCLAIM`

```{r model1createDummy}
trnFreq <- factor(tstX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
trnSev <- tstX$TARGET_AMT
tstDumFreq <- dummyVars(TARGET_FLAG ~ .  + OWN * HOME_VAL +
                          KIDSDRIV * HOMEKIDS + HOME_VAL * INCOME * BLUEBOOK +
                          CLM_FREQ * OLDCLAIM - INDEX - TARGET_AMT,
                        fullRank = TRUE, data = tstX)
tstXD <- predict(tstDumFreq, newdata = tstX)
```

At this point the code will be set up to preprocess the data and train the
model. The two pre-processing steps which will be done will be to check for
near-zero variance between the predictors and then use kNN imputations for
missing values. The actual code may be found in the CODE APPENDIX.

```{r runModel1Freq}
trC <- trainControl(method = 'none',            # Using StepAIC
                    classProbs = TRUE,          # Classification
                    summaryFunction = prSummary # Precision/Recall)
)
set.seed(487)
binlogFit <- train(x = tstXD, y = trnFreq, preProcess = c('nzv', 'knnImpute'),
                   trControl = trC, method = 'glmStepAIC', family = 'binomial',
                   direction = 'both', trace = 0)
kable(summary(binlogFit)$coefficients, digits = 3L,
      caption = "Model 1 Frequency Regression Output")
```

The last trace of the stepping procedure is shown below.
```
                             Df Deviance    AIC
<none>                            2077.4 2135.4
+ YOJ                         1   2075.8 2135.8
- SEX.F                       1   2080.0 2136.0
- JOB.Professional            1   2080.2 2136.2
+ `EDUCATION.High School`     1   2076.2 2136.2
+ JOB.Clerical                1   2076.4 2136.4
+ `JOB.Blue Collar`           1   2076.8 2136.8
+ JOB.Lawyer                  1   2076.9 2136.9
+ `INCOME:HOME_VAL`           1   2076.9 2136.9
+ `HOME_VAL:BLUEBOOK`         1   2077.0 2137.0
+ OLDCLAIM                    1   2077.0 2137.0
+ `INCOME:BLUEBOOK`           1   2077.0 2137.0
- `CAR_TYPE.Panel Truck`      1   2081.2 2137.2
+ RED_CAR.yes                 1   2077.2 2137.2
+ HOMEKIDS                    1   2077.2 2137.2
+ HOME_VAL                    1   2077.3 2137.3
+ `HOME_VAL:OWNYes`           1   2077.3 2137.3
+ AGE                         1   2077.3 2137.3
+ CAR_AGE                     1   2077.4 2137.4
- JOB.Student                 1   2081.8 2137.8
- PARENT1.Yes                 1   2082.4 2138.4
- `INCOME:HOME_VAL:BLUEBOOK`  1   2083.4 2139.4
- `JOB.Home Maker`            1   2083.4 2139.4
- EDUCATION.Bachelors         1   2084.5 2140.5
- `OLDCLAIM:CLM_FREQ`         1   2085.1 2141.1
- CAR_TYPE.SUV                1   2085.8 2141.8
- BLUEBOOK                    1   2086.4 2142.4
- OWN.Yes                     1   2086.5 2142.5
- EDUCATION.Masters           1   2087.2 2143.2
- EDUCATION.PhD               1   2089.8 2145.8
- CAR_TYPE.Pickup             1   2090.1 2146.1
- CAR_TYPE.Van                1   2090.2 2146.2
- TRAVTIME                    1   2090.9 2146.9
- INCOME                      1   2092.0 2148.0
- `CAR_TYPE.Sports Car`       1   2092.1 2148.1
- MSTATUS.No                  1   2093.4 2149.4
- CLM_FREQ                    1   2095.5 2151.5
- TIF                         1   2095.8 2151.8
- KIDSDRIV                    1   2101.1 2157.1
- MVR_PTS                     1   2103.2 2159.2
- CAR_USE.Private             1   2106.4 2162.4
- JOB.Manager                 1   2108.4 2164.4
- REVOKED.Yes                 1   2118.5 2174.5
- URBANICITY.Rural            1   2271.8 2327.8
```

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r zeroVal}
```
```{r statsN}
```
```{r graphsN}
```
```{r graphsF}
```
```{r corrgram}
```
```{r dataClean}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1createDummy}
```
```{r runModel1Freq}
```
